\section{Background}
The background section of the
report should set the project into context by
relating it to existing published work which you
read at the start of the project when your
approach and methods were being considered.
The published work may be in the form of
research papers, articles, text books, technical
manuals, or even existing software or hardware
of which you have had hands-on experience.
Don't be afraid to acknowledge the sources of
your inspiration; you are expected to have seen
and thought about other people's ideas; your
contribution will be putting them into practice in
some other context. \textbf{However, you must avoid
plagiarism}. \\ \newline \noindent You should provide enough background to the reader
for them to understand what the project is all about,
and what is the relevant prior work.\\ \newline \noindent Examiners like to know that you have done the
appropriate background research and it is important
that you review either what has been done previously
to tackle related problems, or perhaps what other
products exist related to your deliverable. Clear
references are important here, and much of this
section will typically already have been written in your
Interim Report. You may use feedback from that
report to improve what you write in your Final Report,
and should note that self-plagiarism between the two
reports is not possible, so no citation is needed of
your own earlier writing.
\begin{itemize}
    \item What does the reader need to know in order
    to understand the rest of the report? What
    problem are you solving?
    \item Why is this problem interesting or worthwhile
    to solve?
    \item Who cares if you solve it?
    \item How does this relate to other work in this
    area?
    \item What work does it build on?
    \item For 'research-style' projects involving the
    design and analysis of specific algorithms
    there is a large amount of relevant
    background both of general theory, and very
    specific to the algorithm you investigate.
    Supervisors will help you to see what is most
    important here, but the general rule is that
    you must both provide overall context and
    note work close to what you do that
    influences your work or is in some way
    comparable to your work.
\end{itemize}
